VM-Centric Snapshot Deduplication\\ for Cloud Data Backup

### 2015-03-13 snapshot_system/mass_intro.tex
re
revise

%Without deduplication,
Source-side deduplication (e.g. ~\cite{Symantec2009})
 eliminates duplicates before backup data is transmitted
to a secondary storage, which saves network bandwidth significantly; however its resource
usage can impact other co-located cloud services. 
It is memory-intensive to compare a large number of fingerprints and identify
duplicates, even optimization or approximation techniques are developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
\comments{
When deleting unused snapshots, a grouped mark-and-sweep approach~\cite{Guo2011}  
is effective while it still carries a significant cost, especially in a distributed
setting. 
} Another side effect of deduplication is the possible loss of failure
resilience~\cite{Reliability06}.  
%Separate files share the same physical copies of blocks that are
%logically duplicated among them.  
If a shared block is lost, all files that
share that block are affected.  
A cloud may offload backup workload from production 
server hosts to dedicated backup proxy servers (e.g. EMC Data Domain) or
backup services (e.g. Amazon S3). This approach simplifies the cluster 
architecture and 
avoids potential performance degradation to production applications when 
backups are in progress.
However, sending out raw and undeduplicated backup data wastes a huge amount
of network bandwidth that would otherwise be available to user VMs. 
\comments{
Even when the storage system implements deduplication internally
such dedicated backup storage is either difficult to scale out
(which can comprise the overall scalability of the converged architecture) 
or it must forego global deduplication in order to gain scalability 
(which increases backup cost).
}

Our work  considers a backup service with source-side deduplication for converged cloud architectures
that is co-located with user VMs, sharing the cloud compute, network, and
storage resource with them.  
This paper extends our preliminary simulation study  in ~\cite{WeiZhangIEEE} to 
restrict the scope of cross-VM deduplication and simplify the deduplication process
by separating popular data chunks and presents the design and implementation of 
a VM-centric backup scheme.  
We term this approach {\em VM-centric} because the deduplication
algorithm considers VM boundaries in making its decisions as opposed to
treating all blocks as being equivalent within the storage system.
Our work focuses on a tradeoff that allows the sharing of only ``popular'' data blocks 
across virtual machines while using localized deduplication within each VM
to achieve both storage savings and fault isolation.
Another issue addressed is fault  isolation in a content sharing environment caused by deduplication.
One consequence of aggressive deduplication is the possible loss of failure
resilience.  If a shared block is lost, all files that
share that block are affected~\cite{Reliability06} and  our work is motivated by this
and develops VM-centric fault isolation techniques.
\comments{
Since the underlying storage file system block size is typically bigger than the average data chunk size
used for deduplication,  packaging
content from different VMs into the same file block  creates a ``false'' sharing that 
affects fault isolation;
}

@@

The rest of this paper is organized as follows.
Section~\ref{sect:background} reviews the background and discusses the  design options for snapshot backup 
with a VM-centric approach. 
%Section~\ref{sect:deduplication}  analyzes the tradeoff and benefits of the VM-centric approach. 
Section~\ref{sect:deduplication}  presents our scheme for  snapshot deduplication. 
%and deletion.
Section~\ref{sect:architecture}  describes a system implementation that evaluates the proposed techniques.
%   the benefit of our approach for fault isolation. 
Section~\ref{sect:evaluation} is our experimental evaluation that compares with other approaches.
Section~\ref{sect:conclusion}  concludes this paper.
The appendix describes an analysis on the snapshot availability of our scheme during storage failures.

>>>>

%Without deduplication,
Source-side deduplication (e.g. ~\cite{Symantec2009})
 eliminates duplicates before backup data is transmitted
to a secondary storage, which saves network bandwidth significantly; however its resource
usage can impact other co-located cloud services. 
It is memory-intensive to compare a large number of fingerprints and identify
duplicates, even with optimization or approximation techniques developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
\comments{
When deleting unused snapshots, a grouped mark-and-sweep approach~\cite{Guo2011}  
is effective while it still carries a significant cost, especially in a distributed
setting. 
} Another side effect of deduplication is the possible loss of failure
resilience~\cite{Reliability06}.  
%Separate files share the same physical copies of blocks that are
%logically duplicated among them.  
If a shared block is lost, all files that
share that block are affected.  
A cloud may offload backup workload from production 
server hosts to dedicated backup proxy servers (e.g. EMC Data Domain) or
backup services (e.g. Amazon S3). This approach simplifies the cluster 
architecture and 
avoids potential performance degradation to production applications when 
backups are in progress.
However, sending out raw and undeduplicated backup data wastes a huge amount
of network bandwidth that would otherwise be available to user VMs. 
\comments{
Even when the storage system implements deduplication internally
such dedicated backup storage is either difficult to scale out
(which can comprise the overall scalability of the converged architecture) 
or it must forego global deduplication in order to gain scalability 
(which increases backup cost).
}

Our work  considers a backup service with source-side deduplication for converged cloud architectures
that is co-located with user VMs, sharing the cloud compute, network, and
storage resource with them.  
This paper extends our preliminary simulation study  in ~\cite{WeiZhangIEEE} to 
restrict the scope of cross-VM deduplication and simplify the deduplication process
by separating popular data chunks and presents the design and implementation of 
a VM-centric backup scheme.  
We term this approach {\em VM-centric} because the deduplication
algorithm considers VM boundaries in making its decisions as opposed to
treating all blocks as being equivalent within the storage system.
Our work focuses on a tradeoff that allows the sharing of only ``popular'' data blocks 
across virtual machines while using localized deduplication within each VM
to achieve both storage savings and fault isolation.
Another issue addressed is fault  isolation in a content sharing environment caused by deduplication.
One consequence of aggressive deduplication is the possible loss of failure
resilience.  If a shared block is lost, all files that
share that block are affected~\cite{Reliability06} and  our work is motivated by this
to develop VM-centric fault isolation techniques.
\comments{
Since the underlying storage file system block size is typically bigger than the average data chunk size
used for deduplication,  packaging
content from different VMs into the same file block  creates a ``false'' sharing that 
affects fault isolation;
}

@@

The rest of this paper is organized as follows.
Section~\ref{sect:background} reviews the background and discusses the  design options for snapshot backup 
with a VM-centric approach. 
%Section~\ref{sect:deduplication}  analyzes the tradeoff and benefits of the VM-centric approach. 
Section~\ref{sect:deduplication}  presents our scheme for  snapshot deduplication. 
%and deletion.
Section~\ref{sect:architecture}  describes a system implementation that evaluates the proposed techniques.
%   the benefit of our approach for fault isolation. 
Section~\ref{sect:evaluation} is our experimental evaluation that compares with other approaches.
Section~\ref{sect:conclusion}  concludes this paper.
The appendix describes an analysis on the deduplication  efficiency with top $k$ popular chunks.
